% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

% from https://tex.stackexchange.com/questions/108658/how-do-i-insert-an-underlined-ordinal-indicator-if-the-font-does-not-have-that
\newcommand{\ula}{\textsuperscript{\b{a}}} % "underlined a in superscript mode"
\newcommand{\ulo}{\textsuperscript{\b{o}}} % "underlined o in superscript mode"


\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{André Albuquerque}{April 4, 1987}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:andre.malbuq.at.gmail.com}{andre.malbuq\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}351-967191550
\\
\noindent\href{https://github.com/amalbuquerque}{github.com/amalbuquerque}\sbull
\href{http://linkedin.com/in/amalbuquerque}{linkedin.com/in/amalbuquerque}
\\
Rua Sá de Miranda 17\sbull
2855-482\thinspace Corroios\sbull
Seixal\sbull
Portugal

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Geek at heart, thoroughly enjoys learning new skills and writing
  quality code to solve interesting challenges. Likes to think about software
  engineering as a collaborative process to solve specific problems in a
  reliable and future-proof way.}
\\
\\
Had his first contact with a computer, a ZX Spectrum+, at the age of three
(1990) and wrote his first lines of code at the age of nine to change the
GORILLA.BAS game bundled with MS-DOS 5, on the 486 computer he got as a
birthday present. Knew from an early age that he wanted to work with computers,
graduated at the age of 22 with a MSc degree in Information Systems and Computer
Engineering from the best engineering school in Portugal.

He is a Senior Staff Engineer at Remote, after working 5 years for two startups.
Previously, he worked on the banking industry for 7 years. During
this banking detour he obtained a MSc degree in Economics.
He is currently helping to develop the Remote product using mostly Elixir
and learning every day about how companies can thrive if the right mix
of collaboration, openness, consistency, goodwill and sound development practices
are applied to every endeavour, big or small.

He co-authored a book on Elixir on 2018,
\href{https://www.packtpub.com/application-development/mastering-elixir}{Mastering
Elixir}, that takes the reader in a journey to develop and deploy on the cloud
a Dropbox-like application, while illustrating intermediate to advanced concepts
like metaprogramming, parallel data processing with back-pressure and deploying
the application to a Kubernetes cluster.
\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\href{https://remote.com}{Remote}}
  {\textsc{Lisbon, Portugal (Fully remote position)}} {%
  \headedsubsection
    {Senior Staff Backend Engineer}
    {Apr \apo24 -- present}
    {\bodytext{Working within our Fintech product area, currently more focused on the interactions between Pricing and other sub-domains like Billing and Payments.
    \begin{itemize}
      \item Gave a talk at AlchemyConf \apo25 about Remote's Elixir monolith
    \end{itemize}}}
}

\headedsection
  {\href{https://remote.com}{Remote}}
  {\textsc{Lisbon, Portugal (Fully remote position)}} {%
  \headedsubsection
    {Staff Backend Engineer}
    {Sep \apo22 -- Mar \apo24}
    {\bodytext{Worked with our Payments teams to deliver robust and compliant payment solutions to our customers across the world.
    \begin{itemize}
      \item Built payment flows allowing multi-currency, different providers and multiple payment methods in record time.
      \item Worked at the intersection of three teams: Payments Core, Employee Payments and Contractor Payments.
    \end{itemize}}}
}

\headedsection
  {\href{https://remote.com}{Remote}}
  {\textsc{Lisbon, Portugal (Fully remote position)}} {%
  \headedsubsection
    {Engineering Technical Lead}
    {Aug \apo21 -- Aug \apo22}
    {\bodytext{Led the Developer Platform team, whose mission is to allow any
    partner to easily integrate the Remote suite of products, and to
    foster and help Remote product teams to expose their features
    through the Remote API.
    \begin{itemize}
      \item The main product is the Remote API, through which we expose
      several features related with the employee lifecycle: onboarding,
      offboarding, time-off and employee details management, etc.
      by the Remote API.
      \item Built an OAuth-based mechanism to allow any Remote user
      to allow its data to be accessed by a Remote API integration.
      \item Built a flexible rate-limiting system depending on the
      type of API client (partner, internal, customer).
      to allow its data to be accessed by a Remote API integration.
      \item Collaborated closely with our partners to ensure the Remote API
      catered to their requirements, and adapted it when needed.
      \item The team is composed by four frontend and backend engineers, a
      product manager and a designer.
    \end{itemize}}}
}

\headedsection
  {\href{https://remote.com}{Remote}}
  {\textsc{Lisbon, Portugal (Fully remote position)}} {%
  \headedsubsection
    {Staff Backend Engineer}
    {May \apo21 -- Aug \apo21}
    {\bodytext{My first goal was to create a public API from scratch,
     that we'll use to expose our product to other parties who want
     to programmatically use it.
    \begin{itemize}
      \item Devised the authentication mechanism, how the API is deployed
      and exposed.
      \item Designed the API interaction with simplicity in mind, while
      abstracting the internal details of the underlying set of features.
      \item After an initial effort with only two engineers,
      we created a full-fledged team (with product, design, frontend and
      backend capabilities) and I assumed its technical leadership.
      \item Proposed and implemented a JSON Schema based solution to validate
      the different payloads received through the API, allowing clients to
      perform the same data validations we do.
    \end{itemize}}}
}

\headedsection
  {\href{https://hopin.com}{Hopin}}
  {\textsc{Lisbon, Portugal (Fully remote position)}} {%
  \headedsubsection
    {Staff Software Engineer}
    {Set \apo19 -- May \apo21}
    {\bodytext{Core Services team,
    a Platform team responsible for cross-cutting concerns like authentication,
    authorization, how to manage users data inside events, and big monolith refactors
    touching other pods areas.
    Assumed Pod Lead responsibilities during a quarter.
    \begin{itemize}
      \item Implemented a roles and permissions system to
	enable event organisers to assign different permissions to event or
	organization administrators.
      \item Contributed to the planning and development of the user data-segregation project,
	ensuring every piece of user data produced by an attendee inside an event is scoped by event.
    \end{itemize}}}
}

\headedsection
  {\href{https://onfido.com}{Onfido}}
  {\textsc{Lisbon, Portugal}} {%
  \headedsubsection
    {Senior Software Engineer - Team Lead}
    {Aug \apo19 -- Set \apo20}
    {\bodytext{Team Lead of the Operations Tech team,
    whose mission is to improve all internal systems to better enable the
    business for the rapid growth phase we're experiencing.
    \begin{itemize}
      \item Started with a complete revamp of the billing system, by removing the
        existing billing logic from our Rails monolith and creating two new
        Elixir microservices. The billing system is now event-based and region agnostic
        using Amazon's SNS and SQS infrastructure.
      \item Deliver a new internal system for account management, replacing the
        legacy experience and automating all the information queries by
        interfacing with Salesforce.
      \item Use this opportunity to refactor a big chunk of the Rails monolith,
        improving the user experience of our internal users and significantly
        reducing tech debt.
    \end{itemize}}}
    
  \headedsubsection
    {Senior Software Engineer}
    {Aug \apo18 -- Aug \apo19}
    {\bodytext{Software engineer on the Distributed Identity team,
    exploring new ways of providing Identity-based services to our customers.
    Analysing different identity solutions and implementing prototypes to better
    understand the technologies under scrutiny.
    \begin{itemize}
      \item Implemented an identity credentialing system based on
        \href{https://www.uport.me}{Uport} solution, that integrated
        with Onfido identity verification platform.
      \item Implemented an identity credentialing system using
        \href{https://www.evernym.com}{Evernym}, that integrated
        with Onfido identity verification platform.
    \end{itemize}
    }}

  \headedsubsection
    {Software Engineer}
    {Oct \apo16 -- Aug \apo18}
    {\bodytext{Software engineer on the Identify and later Biometrics team,
    maintaining our current provider integrations living in our Ruby on Rails
    monolith platform and creating new integrations/migrating old ones to new
    microservices in Ruby and Elixir.
    \begin{itemize}
      \item Created a \href{https://goo.gl/X5bafF}{new \acr{S3} document storage
        microservice}, using Elixir processes to implement a caching mechanism
        and performing the encryption/decryption tasks. Its usage reduced the
        network bandwidth of our document processing pipeline from 20 Mbps to
        ~300Kbps.
      \item Implemented the mechanism in Elixir that calls all the algorithms
        developed in-house and our external providers in parallel and later
        aggregates the different results.
      \item Extracted several provider integrations from our monolith to new
        microservices written in Ruby.
      \item Used an AWS API Gateway + Lambda to create a secure callback
        mechanism, allowing an external provider to asynchronously reply to us.
    \end{itemize}}}
}

\headedsection
  {\href{https://www.bportugal.pt/}{Bank of Portugal, Payment Systems Department}}
  {\textsc{Lisbon, Portugal}} {%
  \headedsubsection
    {IT Expert, Advisor}
    {Sept \apo14 -- Sept \apo16}
    {\bodytext{Overseer on the Payment Systems Department, advising and
    providing insights on \acr{IT} subjects: \acr{SWIFT} Continuity, Cyber
    security in \acr{FMI}s,
    digital currencies, online payment solutions, development of new information
    systems. Represented the central bank on the \acr{ECB} Oversight Group assessing
    the \acr{SEPA} Direct Debit Scheme compliance.
    \begin{itemize}
      \item Wrote a comprehensive study on blockchain technology (82 pages), virtual
        currencies and their possible risks and impact on the financial system.
    \end{itemize}}}
}

\headedsection
  {\href{https://www.bportugal.pt/}{Bank of Portugal, Information Systems and
  Technology Department}}
  {\textsc{Lisbon, Portugal}} {%
  \headedsubsection
    {Team Leader}
    {Jan \apo11 -- Sept \apo14}
    {\bodytext{Team leader on the \acr{IT} Department, performed requirements
    analysis, improved and maintained some of our legacy systems. Defined the
    architecture of new projects and routinely supported the deployment of new
    versions to production environments.
    \begin{itemize}
      \item Developed several Web Services interfaces (using an \acr{ESB} as a proxy when needed)
        within different applications to fetch the \acr{ECB}\apo s machine
        lists. \acr{XSD}, \acr{WSDL}, \acr{SOAP}, \acr{ASP.NET} Web Services,
        \acr{TLS}/\nsp\acr{SSL} certificates.
      \item Did the maintenance and new developments of the eligible assets
        database application, a Java web application. Spring Framework
        (\acr{MVC}, \acr{IoC}, Security -- using LDAP --,
        \acr{JPA}), Hibernate 3, MySQL, \acr{SVN}.
      \item Contributed to the requirements analysis, defined the architecture
        and further development of two \acr{ASP.NET MVC} web applications,
        allowing the banks to report information via extranet and its subsequent
        analysis using an intranet web app. \acr{ASP.NET MVC 3}, \acr{NUnit},
        Microsoft \acr{SQL} Server, jQuery, \acr{TFS}.
      \item Did the maintenance, new developments (as well as support and
        on-call tasks) of our most critical system, \acr{TARGET2-PT}, our
        integration with the European real-time gross settlement system.
        \acr{ASP.NET} Web Forms, Microsoft \acr{SQL} Server, Sybase, WebSphere
        \acr{MQ}, SourceSafe.
    \end{itemize}}}
}


\headedsection
  {\href{https://www.boldint.com/}{BOLD International}}
  {\textsc{Lisbon, Portugal}} {%
  \headedsubsection
    {IT Consultant}
    {Oct \apo10 -- Jan \apo11}
    {\bodytext{Developed a web application to support and enhance the Technical
    Support Front Office of the main Portuguese Telco. ExtJS, Spring Framework
    (\acr{MVC}, \acr{IoC}, Security), Java \acr{EE} (\acr{EJB} 3.0, HornetQ,
    \acr{JPA}), Oracle \acr{DB}, JBoss 5.1, \acr{BPM}.
    }}
}


\headedsection
  {\href{https://www.everis.com/global/en}{everis}}
  {\textsc{Lisbon, Portugal}} {%
  \headedsubsection
    {Consultant}
    {Sept \apo09 -- Sept \apo10}
    {\bodytext{Performed the functional certification of the software developed
    in-house in a medium-sized Portuguese bank. \acr{AS}/400 (\acr{IBM} System
    i), \acr{DB2}.
    }}
}


\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to
  \href{http://www.linkedin.com/in/amalbuquerque}{André's LinkedIn profile} for a more complete list of work experience along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.iseg.ulisboa.pt/?locale=en}{School of Economics \&\
  Management \textemdash Univ.
  de Lisboa}}
  {\textsc{Lisbon, Portugal}} {%
  \headedsubsection
    {MSc in Monetary and Financial Economics}
    {Sept \apo14 -- Oct \apo16}
    {\bodytext{Master thesis on the determinants of sovereign ratings using
    Stata. You can find a working paper based on my dissertation
    \href{http://hdl.handle.net/10400.5/13134}{here}.}}
    {\bodytext{Coursework: Macroeconomics; Microeconomics; Econometrics;
    Monetary Policy; Behavioral Finance; Public Finance; Macroeconomics and
    Monetary Theory; Financial Economics; Financial Markets.
    }}
}

\headedsection
  {\href{https://tecnico.ulisboa.pt/en}{Instituto Superior Técnico \textemdash Univ.
  de Lisboa}}
  {\textsc{Lisbon, Portugal}} {%
  \headedsubsection
    {MSc in Information Systems and Computer Engineering, 15/\,20}
    {Sept \apo07 -- Oct \apo09}
    {\bodytext{Major in Distributed
    Systems, minor in Software Engineering.}}
    {\bodytext{Coursework: Software Architecture;
    Software Quality; Virtual Execution Environments; Mobile Computing; Network
    and Computers Security; Parallel and Distributed Computing.
    }}

  \headedsubsection
    {BSc in Information Systems and Computer Engineering, 15/\,20}
    {Sept \apo04 -- Jul \apo07}
    {\bodytext{Coursework: Software Engineering; Operating Systems; Databases;
    Computer Architecture; Analysis and Synthesis of Algorithms; Artificial
    Intelligence; Compilers; Computer Networks; Physics; Calculus; Algebra.
    }}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Likes to collaborate closely with Product, using continuous delivery whenever
  possible (knowledgeable about Gitlab CI, Jenkins and Travis CI). Likes functional programming, enjoys working with Elixir/\nsp Ruby/\nsp Python/\nsp C$^\sharp$ and Node.js.
  Experienced with Phoenix and Rails web frameworks,
  virtualization, containers (Docker, Kubernetes and several \acr{AWS}
  services) and DevOps (Terraform). Linux and vim user. Loves Git.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Portuguese \emph{(mother tongue)} and English \emph{(full professional proficiency)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {basketball, gymnastics, behavioral economics, embedded programming, custom
  and vintage keyboards, music, philosophy, privacy in the age of internet,
  running, travel, vim.}

\end{document}
